Differential invariant signatures for planar Lie group transformations of images

### 2020-11-17 paper/newpaper.tex
progress

@@

%Groups we've done:
%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
\subsection{Example signatures}

\section{Differential invariants through tensor contraction}
\label{sec:contraction}

@@

\noindent where $\alpha_1 = b g + 2 a h, \alpha_2 = 2 b g + a h$, $\beta_1 = d g + 2 c h, \beta_2 = 2 d g + c h$, $\gamma_1 = b c + 2 a d, \gamma_2= 2 b c + a d$, and $\delta_1 = (b c g+a d g+a c h), \delta_2 = (b d g+b c h+a d h)$.
%\left[
%\begin{array}{ccccccccc}
 %a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 %b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 %-2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 %-b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 %-2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 %6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 %2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
   %g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
 %2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
   %c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
 %6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
%\end{array}
%\right]

%%A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.  That is, $D$ is a relative invariant of weight 2 of this action. 
%Both $D$ and $E$ will be useful quantities shortly, but note that, from (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on its sign.

We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that $D$ and $\bar f_{\bar y \bar y}$ have the same sign; in what follows we assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$

@@

Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants. We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)\:,$$ where (with $P_n$ denoting a polynomial of degree $n$):
$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.$$

>>>>

\subsection{Example signatures}

@@

%Groups we've done:
%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
\section{Differential invariants through tensor contraction}
\label{sec:contraction}

@@

\noindent where $\alpha_1 = b g + 2 a h, \alpha_2 = 2 b g + a h$, $\beta_1 = d g + 2 c h, \beta_2 = 2 d g + c h$, $\gamma_1 = b c + 2 a d, \gamma_2= 2 b c + a d$, and $\delta_1 = (b c g+a d g+a c h), \delta_2 = (b d g+b c h+a d h)$.

We begin the construction of the moving frame by choosing $\bar f_{\bar x}
= 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a =
(1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that
$\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2
f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of
$A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that $D$ and
$\bar f_{\bar y \bar y}$ have the same sign. If $D < 0$, we choose the
frame $\bar{f}_{\bar y \bar y} = -1$ and if $D \ge 0$ we choose $\bar
f_{\bar y \bar y} = 1$. Then $d = f_x/|D|^{1/2}.$

@@

Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants. We choose: 
\begin{equation*}
 (\bar f_{\bar x\bar x\bar x}, \bar f_{\bar x\bar x\bar y}^2, \bar f_{\bar
 x\bar y\bar
 y})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right).
\end{equation*} 
\todo[inline]{Check J2 has squared or not}
The terms $J_1, J_2, J_3$ can be written in terms of $D$ and $E$, together
with a polynomial of degree $n$ denoted by $P_n$. 
\begin{equation*}
    J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.
\end{equation*}
